### 2023-04-25 paper.Rmd
editing

An exclusive maximization of $\mathit{SSE_{Var}}$ (i.e., equalizing variances) is not feasible---and most likely not interesting on its own---without also considering the standard $\mathit{SSE}$ (i.e., equalizing means). Hence, when striving for similarity in group variances by maximizing $\mathit{SSE_{Var}}$, it is at the same time necessary and worthwhile to strive for similarity in means, and thus to maximize $\mathit{SSE}$ at the same time. The most simple approach for an optimization that considers multiple criteria at the same time is the weighted sum approach [@naidu2014; @marler2010]. That is, all criteria are computed independently from each other and are then combined into a single criterion through a weighted sum; a suitable optimization algorithm is then used to maximize the combined criterion. By combining $\mathit{SSE_{Var}}$ and $\mathit{SSE}$ in a single criterion, we define the objective function for k-plus anticlustering:

@@

```{r}
final_tab_sim1 <- round(Reduce("+", results) / length(results) * 100, 2)
rownames(final_tab_sim1) <- c(
  "$\\mathbf{w} = (1, 1, 1, 1)$ / unstandardized",
  "$\\mathbf{w} = (1, 1, 1, 1)$ / standardized",
  "$\\mathbf{w} = (10, 1, 1, 1)$",
  "$\\mathbf{w} = (1, 10, 1, 1)$",
  "$\\mathbf{w} = (1, 1, 10, 1)$",
  "$\\mathbf{w} = (1, 1, 1, 10)$"
)
colnames(final_tab_sim1) <- c(
  "$\\mathit{SSE}$",
  "$\\mathit{SSE_{Var}}$", 
  "$\\mathit{SSE_{Skew}}$",
  "$\\mathit{SSE_{Kurtosis}}$",
  "Average"
)
note <- paste0("Cells indicate how well the maximization $\\mathit{SSE_{kplusGeneralized}}$ fulfilled each of the four constituting criteria $\\mathit{SSE}$, $\\mathit{SSE_{Var}}$, $\\mathit{SSE_{Skew}}$, and $\\mathit{SSE_{Kurtosis}}$, depending on the weighting scheme. For each simulation run, the relative performance was computed as the $\\mathit{SSE}$ that was obtained by the given weighting scheme, divided by the best $\\mathit{SSE}$ that was obtained by any weighting scheme in this simulation run. Cell values represent the average relative performance across all ", length(results), " simulation runs.")

@@

This section demonstrates how readers can easily employ k-plus anticlustering using the R package `anticlust` [@papenberg2020] using the function `kplus_anticlustering()`, which implements the unweighted sum approach for k-plus anticlustering. The package can be installed in the R environment using the `install.packages()` command:

@@

>>>>

An exclusive maximization of $\mathit{SSE_{Var}}$ (i.e., equalizing variances) is not feasible---and most likely not interesting on its own---without also considering the standard $\mathit{SSE}$ (i.e., equalizing means). The most simple approach for an optimization that considers multiple criteria at the same time is the weighted sum approach [@naidu2014; @marler2010]. That is, all criteria are computed independently from each other and are then combined into a single criterion through a weighted sum; a suitable optimization algorithm is then used to maximize the combined criterion. By combining $\mathit{SSE_{Var}}$ and $\mathit{SSE}$ in a single criterion, we define the objective function for k-plus anticlustering:

@@

```{r}
final_tab_sim1 <- round(Reduce("+", results) / length(results) * 100, 2)
rownames(final_tab_sim1) <- c(
  "$\\mathbf{w} = (1, 1, 1, 1)$ / unstandardized",
  "$\\mathbf{w} = (1, 1, 1, 1)$ / standardized",
  "$\\mathbf{w} = (10, 1, 1, 1)$",
  "$\\mathbf{w} = (1, 10, 1, 1)$",
  "$\\mathbf{w} = (1, 1, 10, 1)$",
  "$\\mathbf{w} = (1, 1, 1, 10)$"
)
colnames(final_tab_sim1) <- c(
  "$\\mathit{SSE}$",
  "$\\mathit{SSE_{Var}}$", 
  "$\\mathit{SSE_{Skew}}$",
  "$\\mathit{SSE_{Kurtosis}}$",
  "Average"
)
note <- paste0("Cells indicate how well the maximization of $\\mathit{SSE_{kplusGeneralized}}$ fulfilled each of the four constituting criteria $\\mathit{SSE}$, $\\mathit{SSE_{Var}}$, $\\mathit{SSE_{Skew}}$, and $\\mathit{SSE_{Kurtosis}}$, depending on the weighting scheme. For each simulation run, the relative performance was computed as the $\\mathit{SSE}$ that was obtained by the given weighting scheme, divided by the best $\\mathit{SSE}$ that was obtained by any weighting scheme in this simulation run. Cell values represent the average relative performance across all ", length(results), " simulation runs.")

@@

This section demonstrates how readers can easily employ k-plus anticlustering using the R package `anticlust` [@papenberg2020]. The package can be installed in the R environment using the `install.packages()` command.

@@

The function `kplus_anticlustering()` available in `anticlust` implements the unweighted sum approach for k-plus anticlustering.
